---
title: "Boosting Practice"
author: "Jinwoo Chung"
output: html_document
---

### Table of Contents
Using spam mail data from kernlab
1. Separate Test and Train Data
2. Model with xgboost
3. Predict and Create Confusion Matrix
4. Find how much Weight each Variable Has
5. Use 5-fold CV to find the best Model
6. Predict and Create Confusion Matrix for the new Model

```{r}
library(pacman)
pacman::p_load(dplyr,xgboost,gbm,caret,rpart,kernlab)
# looking at overall look of the data
data(spam)
glimpse(spam)
```

### Separate Test and Train Data

Have to slighly alter data before inserting into the model
```{r}
mail <- spam
mail$type <- ifelse(mail$type=='spam', 1, 0)
# setting seed
set.seed(77)
# splitting data
index.train <- sample(1:nrow(mail), round(nrow(mail) * 0.8))
train <- mail[index.train, ]
test <- mail[-index.train, ]
# looking at the overall data
glimpse(train)
```

### Model with xgboost

```{r}
train.boost <- xgboost(data=data.matrix(train[,-58]), label=train[,58], max_depth=4,
                       eta=0.2, nrounds=500, objective='multi:softmax', num_class=2)
```

### Predict and Create Confusion Matrix

```{r}
# predicting
pred.spam <- predict(train.boost, newdata=data.matrix(test[,-58]), ntreelimit=500)
# confusion matrix
caret::confusionMatrix(as.factor(ifelse(pred.spam==1, "spam", "nospam")), as.factor(ifelse(test[,58]==1, "spam", "nospam")))
```

### Find how much Weight each Variable Has

Finding Weights
```{r}
weight.spam <- xgboost::xgb.importance(feature_names=colnames(spam)[1:ncol(spam)-1], model=train.boost)
weight.spam
```

Plotting for Visualization
```{r}
xgboost::xgb.plot.importance(importance_matrix = weight.spam, top_n = 25)
```

### Use 5-fold CV to find the best Model
```{r}
train.cv <- trainControl(method="cv", number=5)
grid = expand.grid(gamma=0, colsample_bytree=1, min_child_weight=1, subsample=1, 
                   max_depth=c(3, 4, 5), eta=c(0.1, 0.2, 0.3), nrounds=500)

spam.boost.caret <- train(x = data.matrix(train[,-58]), y=as.factor(train[,58]),
                     trControl=train.cv, tuneGrid=grid, method="xgbTree")

print(spam.boost.caret)
```

### Predict and Create Confusion Matrix for the new Model
```{r}
pred.spam.caret <- predict(spam.boost.caret, newdata=data.matrix(test[,-58]), ntreelimit=500)
confusionMatrix(as.factor(ifelse(pred.spam.caret==1, "spam", "nospam")), as.factor(ifelse(test[,58]==1, "spam", "nospam")))
```






