---
title: "k-NN Practice (Basic)"
author: "Jinwoo Chung"
output: html_document
---
## Table of Contents
1. Setup
2. Separate Train and Test Data
3. Use caret::train to find the optimal k for k-NN
4. Confusion Matrix of the Result from k-NN

### Setup
```{r}
library(pacman)
pacman::p_load(data.table,dplyr,caret,class)
main <- as.data.frame(data.table::fread("https://raw.githubusercontent.com/Jinwooooo/fcdc-ml-practice/master/data/01_heights_weights_genders.csv"))
# due to Gender values being a character value, reformatting them into a factor for regression
```

### Separate Train and Test Data
```{r}
# setting seed
set.seed(30)
# splitting data
# can also use caret::createDataPartition(main$Gender, p = 0.8, list = FALSE) for completely random set
index.train <- sample(1:nrow(main), round(nrow(main) * 0.8))
train <- main[index.train,]
test <- main[-index.train,]
glimpse(train)
```

### Use caret::train to find the optimal k for k-NN
```{r}
# doing 3-fold cv
ctrl <- caret::trainControl(method='repeatedcv', repeats=3)
# default k values are from 5~9, in order to do wider range of k, need to expand the k grid
grid <- expand.grid(k=c(1,3,5,7,10,15,20,25,30))
optimal.k <- caret::train(Gender ~ ., data=train, method='knn', trControl=ctrl, tuneGrid = grid)
plot(optimal.k)
```

Optimal Value : k = 7

### k-NN Result and Confusion Matrix
```{r}
knn7.train <- class::knn(train=train[,2:3], test=test[,2:3], cl=train[,1], k=7)
caret::confusionMatrix(knn7.train, as.factor(test[,1]))
```

#### Conclusion
Accuracy is fairly high (91.75%), but the Kappa value is not as high. Overall kNN seems to be a good fit for this data set








