---
title: "Naive Bayes Practice"
author: "Jinwoo Chung"
output: html_document
---

## Table of Contents
1. Setup
2. Separate Train and Test Data
3. Create Naive Bayes Model
4. Create Confusion Matrix
5. Use caret package to find accuracy of the model (i.e. do Cross Validation)

### Setup
```{r}
library(pacman)
pacman::p_load(caret,naivebayes,data.table,dplyr)
main <- as.data.frame(data.table::fread('https://raw.githubusercontent.com/Jinwooooo/fcdc-ml-practice/master/data/titanic-train.csv'))
# as all inputs in naive bayes model must be quantitative (and boolean...), 
# need to drop and reformat some columns
```

Before chopping off and modifying data...
```{r}
glimpse(main)
# removing part
removing.cols <- c('PassengerId','Name','Ticket','Cabin','Fare')
main <- main[,(!(colnames(main) %in% removing.cols))]
# changing qualitative data (more like strings...) -> quantitative data
# bayes model does not work with continuous data, so will change age into 2 factors (child and adult)
main$Age <- ifelse(main$Age < 20, 'child', 'adult')
main[colnames(main)] <- lapply(main[colnames(main)], as.factor)
```

After modification...
```{r}
glimpse(main)
```

### Separate Train and Test Data
```{r}
# setting seed
set.seed(33)
# splitting data
index.train <- sample(1:nrow(main), round(nrow(main) * 0.8))
train <- main[index.train, ]
test <- main[-index.train, ]
# looking at the overall data
glimpse(train)
```

### Create Naive Bayes Model
```{r}
nb.train <- naive_bayes(x = train[,-1], y = train[,1])
nb.train
```

### Create Confusion Matrix
```{r}
prediction <- predict(nb.train, test)
confusionMatrix(prediction, as.factor(test$Survived))
```

## Use caret package to find accuracy of the model (i.e. do Cross Validation)
```{r}
# 10-fold
ctrl <- caret::trainControl(method="cv", number=10)
# naivebayes Package
nb.cv10.train <- caret::train(x = train[,-1], y = train[,1], trControl=ctrl, method="naive_bayes")
print(nb.cv10.train)
```

This is one of the major downside of using naive bayes. While other ML models have variables that you can tweak so
that the results can be enhanced, Naive Bayes if used and turns out the model isn't very good, then this model cannot
be used for that dataset.






