---
title: "SVM Practice"
author: "Jinwoo Chung"
output: html_document
---

### Table of Contents
Using iris (comes w/ basic package) data, no need to setup data
1. Separate Test and Train Data
2. Use Linear and Radial Kernel for Model and Create Confusion Matrix
3. Use 5-fold CV and Bootstrap to find the best Model
4. By using the best Model, Predict and Create Confusion Matrix

```{r}
library(pacman)
pacman::p_load(dplyr,caret,e1071)
# looking at overall look of the data
glimpse(iris)
```

### Separate Test and Train Data
```{r}
# setting seed
set.seed(55)
# splitting data
index.train <- sample(1:nrow(iris), round(nrow(iris) * 0.8))
train <- iris[index.train, ]
test <- iris[-index.train, ]
# looking at the overall data
glimpse(train)
```

### Use Linear and Radial Kernel for Model and Create Confusion Matrix

Linear (Model)
```{r}
svm.linear.train <- svm(Species ~ ., data=iris, kernel='linear')
summary(svm.linear.train)
```

Linear (Plotting for Sepal)
```{r}
# need to do slice in order to show 3 different species, if not it will separate line in the middle
# the data points will still be separated visually though
plot(svm.linear.train, test, Petal.Width ~ Petal.Length, slice = list(Sepal.Width = 3, Sepal.Length = 4))
```

Can do this with Petal as well to find how well the model does for this dataset.

Linear (Confusion Matrix)
```{r}
prediction.linear.train <- predict(svm.linear.train, test)
confusionMatrix(prediction.linear.train, test$Species)
```

Radial (Model)
```{r}
svm.radial.train <- svm(Species ~ ., data=iris, kernel='radial')
summary(svm.radial.train)
```

Radial (Plotting for Sepal)
```{r}
plot(svm.radial.train, test, Petal.Width ~ Petal.Length, slice = list(Sepal.Width = 2, Sepal.Length = 3.5))
```

Radial (Confusion Matrix)
```{r}
prediction.radial.train <- predict(svm.radial.train, test)
confusionMatrix(prediction.radial.train, test$Species)
```

### Use 5-fold CV and Bootstrap to find the best Model
Linear (5-fold)
```{r}
svm.cv.linear <- tune(svm, Species ~ ., data = iris, kernel="linear", ranges = list(cost = 2^(-1:4)), 
                      tunecontrol = tune.control(sampling = "cross", cross=5))
plot(svm.cv.linear)
svm.cv.linear$best.performance
```

Radial (5-fold)
```{r}
svm.cv.radial <- tune(svm, Species ~ ., data = iris, kernel="radial", ranges = list(gamma = 2^(-5:1), cost = 2^(-1:4)), 
                      tunecontrol = tune.control(sampling = "cross", cross=5))
plot(svm.cv.radial)
svm.cv.radial$best.performance
```

Linear (bootstrap)
```{r}
svm.bs.linear <- tune(svm, Species ~ ., data = iris, kernel="linear", ranges = list(cost = 2^(-1:4)), 
                      tunecontrol = tune.control(sampling = "bootstrap", boot.size=0.8, nboot=5))
plot(svm.bs.linear)
svm.bs.linear$best.performance
```

Radial (bootstrap)
```{r}
svm.bs.radial <- tune(svm, Species ~ ., data = iris, kernel="radial", ranges = list(gamma = 2^(-5:1), cost = 2^(-1:4)), 
                      tunecontrol = tune.control(sampling = "bootstrap", boot.size=0.8, nboot=5))
plot(svm.bs.radial)
svm.bs.radial$best.performance
```

Seems like linear bootstrap did the best as it's error is the lowest on best performance

### By using the best Model, Predict and Create Confusion Matrix

Linear (Best Model)
```{r}
svm.bs.linear$best.model
```

Linear (Plotting for Sepal)
```{r}
plot(svm.bs.linear$best.model, test, Sepal.Width ~ Sepal.Length,
     slice = list(Petal.Width = 0.5, Petal.Length = 3))
```

Linear (Confusion Matrix)
```{r}
prediction.linear.best.train <- predict(svm.bs.linear$best.model, test)
confusionMatrix(prediction.linear.best.train, test$Species)
```














